---
title: Race and Inarceration rate
author: Rona Guo
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# library(knitr)
#library(tidyverse)
#library(ggplot2)
#library(maps)
#library(kableExtra)

# Source the data
source("analysis.R")
```

The evidence of institutional racism and incarceration is painfully obviously 
when we look at the incarceration rates among different races in the United 
States. It was and still is a problem that POC, especially Black people, face today. 

I decided to focus on the incarceration rate. By comparing the rates, which is 
the percent of people in jail or prison out of the total population age 15
to 64 of that race, as this age group is the most likely to be incarcerated,
for overall population, Black, White, Latinx, and Native people.


# Summary information for WA
Here is a comparison of incarceration rate in Washington State.
```{r, echo = F, message=FALSE}
knitr::kable(incarceration_table, format = "html", table.attr = "style='width:80%;'")

```


# Time trend plot
Here is a comparison of average incarceration rate across the nation from 2000 to 2018.
```{r, echo = F}
time_trned_plot

```


# Variable comparison chart
This is the plot for 10 states with the highest black incarceration rate. Each 
color represents a different race.
```{r, echo = F}
state_plot

```

# Incarceration ratio map of US
This is the ratio of Black incarceration rate compare to overall.
```{r, echo = F}
disparity_map
```